\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-24 notes/2loopNLSM.tex
Rework of intro to YangMills revisited.

%Comment commands
\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{#1}}}
\newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
\newcommand{\draftnoteJM}[1]{\textbf{\textcolor{blue}{#1}}}

@@

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions in searching for double-copyable integrand numerators (ordered accoring to the
reference):
\begin{enumerate}
\item Locality: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item Power-counting: The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item Cubic diagrams: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item Relabeling : The diagram numerators are only a function of the
  diagram's topology and labeling.
\item Symmetries: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item Unitarity cuts: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item Color-kinematics duality: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}
Point 1 is generally a matter of convenience: there are many examples
in which ``numerators'' with controlled rational contributions have
been found \citepls{}.  However, without a guiding principle about
what types of rational terms to use, the size of ans\"{a}tze quickly
get out of hand.  Point 2 was motivated at the time by the hope that
color-dual numerators could arise naturally out of a special gauge
choice.  However, recent work by Ben-Shahar, Garozzo, and Johansson
\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
demonstrates that constructing Feynman rules which produce manifestly
color-dual numerators for the NMHV sector of Yang--Mills requires
introducing additional auxiliary fields, including higher-spin modes,
which could shift the expected power counting in non-trivial ways.
Point 3 is a requirement of the BCJ double-copy: currently there is no
known way of incorporating non-cubic diagrams into the kinematic
Jacobi relations.  Points 4 and 5 will be elaborated on in
\cref{sec:syms}, Point 6 in \cref{sec:unitarity}, and Point 7 in
\cref{sec:jac-rels}.

@@

Different kinds of CK.
We want global.
Global is the simplest option, it is also the option that you would automatically get if you had a color-dual Lagrangian.
By ``global'' we mean that color-kinematics duality is satisfied in any kinematic configuration of the integrand.
This is a much more stringent condition than absolutely necessary.
There is reason to believe (cite Zvi et al) that global numerators cannot always be found.
One resolution to the issue is to only demand color-kinematics duality on the unitarity cuts of the integrand, i.e., in specific kinematic limits.
Enforcing Jacobi on the cuts is enough to ensure that the squared integrand will correctly cut to gravity (or whatever the squared theory might be).
When a globally color-dual numerator cannot be found, another alternative explored in the literature is to increase the size of the numerator ansatz by enlarging the numerator from a polynomial to a rational function with spurious singularities (cite Donal et al).
When global color-kinematics fails, the hope is that it can be restored by enlarging the size of the ansatz, either by giving the numerator of each graph its own ansatz (first option described) or by promoting the numerator to a non-local function (second option described).
Note that a theory whose Lagrangian has color-kinematics duality would naturally produce a globally color-dual integrand so the quest for a global numerator is closely related to the existence of a Lagrangian exhibiting color-kinematics duality.
Section X is devoted to color-dual representations of the 4pt 2-loop NLSM integrand and the analogous integrand for YM is treated in section Y.
Two-loop color-dual integrands for pure YM have been investigated before but only for a limited ansatz that manifests locality (cite Zvi et al paper).
All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

@@

\subsection{Yang-Mills revisited -- Alex}
Transition paragraph.....

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) lay out the following core assumptions for
integrand numerators (in addition to obeying some form of the
kinematic Jacobi relations) \cite{Bern:2015ooa}
\begin{enumerate}
\item Locality: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams. \emph{We explore a minor breaking of this assumption}
\item Power-counting: The maximum power of the loop momenta in the
  numerator is boudned by Feynman-gauge Feynman rules.  \emph{We
    explore breaking this assumption}.
\item Cubic diagrams: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item Relabeling : The diagram numerators are only a function of the
  diagram's topology and labeling
\item Symmetries: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}
\item Unitarity cuts: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\end{enumerate}
They demonstrated that the above assumptions are incompatible with an
off-shell solution to the kinematic Jacobi relations.  Here, we
explore two violations of these core assumptions.

First, we analyze the power-counting assumption.  In our labeling of
the two loop Jacobi-basis diagrams, shown in \ace{Figure out fig}, we
find that the power counting bound proposed by Bern, Davies, and Nohle
leads to an initial ansatz with XX terms in the double-box, and YY
terms for the penta-triangle.  However, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?} demonstrates that constructing Feynman rules that
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  We therefore attempt to find an
off-shell color-dual Yang--Mills representation in which all power
counting restrictions are lifted.

>>>>

%Comment commands
\newcommand{\ace}[1]{\textcolor{darkgreen}{\textbf{AE:}{ #1}}}
\newcommand{\nhp}[1]{\textcolor{nhpRed}{\textbf{NHP:}{#1}}}
\newcommand{\draftnoteJM}[1]{\textbf{\textcolor{blue}{#1}}}

@@

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions in searching for double-copyable integrand numerators (ordered accoring to the
reference):
\begin{enumerate}
\item Locality: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item Power-counting: The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item Cubic diagrams: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item Relabeling : The diagram numerators are only a function of the
  diagram's topology and labeling.
\item Symmetries: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item Unitarity cuts: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item Color-kinematics duality: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}
Point 1 is generally a matter of convenience: there are many examples
in which ``numerators'' with controlled rational contributions have
been found
\cite{Square,WeinzierlBCJLagrangian,Mogull:2015adi,FivePointN4BCJ,Johansson:2017bfl}.
However, without a guiding principle about what types of rational
terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
2 was motivated at the time by the hope that color-dual numerators
could arise naturally out of a special gauge choice.  On the other hand, recent
work by Ben-Shahar, Garozzo, and Johansson \cite{Ben-Shahar:2022ixa}
\ace{Are there other good examples?}  demonstrates that constructing
Feynman rules which produce manifestly color-dual numerators for the
NMHV sector of Yang--Mills requires introducing additional auxiliary
fields, including higher-spin modes, which could shift the expected
power counting in non-trivial ways.  Point 3 is a requirement of the
BCJ double-copy: currently there is no known way of incorporating
non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
5 will be elaborated on in \cref{sec:syms}, Point 6 in
\cref{sec:unitarity}, and Point 7 in \cref{sec:jac-rels}.

@@

Different kinds of CK.  We want global.  Global is the simplest
option, it is also the option that you would automatically get if you
had a color-dual Lagrangian.  By ``global'' we mean that
color-kinematics duality is satisfied in any kinematic configuration
of the integrand.  This is a much more stringent condition than
absolutely necessary.  There is reason to believe \cite{Bern:2015ooa}
\ace{Is this the cite you wanted?}  that global numerators cannot
always be found.  One resolution to the issue is to only demand
color-kinematics duality on the unitarity cuts of the integrand, i.e.,
in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
to ensure that the squared integrand will correctly cut to gravity (or
whatever the squared theory might be).  When a globally color-dual
numerator cannot be found, another alternative explored in the
literature is to increase the size of the numerator ansatz by
enlarging the numerator from a polynomial to a rational function with
spurious singularities (cite Donal et al).  When global
color-kinematics fails, the hope is that it can be restored by
enlarging the size of the ansatz, either by giving the numerator of
each graph its own ansatz (first option described) or by promoting the
numerator to a non-local function (second option described).  Note
that a theory whose Lagrangian has color-kinematics duality would
naturally produce a globally color-dual integrand so the quest for a
global numerator is closely related to the existence of a Lagrangian
exhibiting color-kinematics duality.  Section X is devoted to
color-dual representations of the 4pt 2-loop NLSM integrand and the
analogous integrand for YM is treated in section Y.  Two-loop
color-dual integrands for pure YM have been investigated before but
only for a limited ansatz that manifests locality (cite Zvi et al
paper).  All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

@@

\subsection{Yang-Mills revisited -- Alex}
Given the close ties between pion and gluon scattering for trees and
at one loop, the success of a globally color-dual solution for pions
at two loops warrants a reexamination of the two-loop pure Yang--Mills
problem.  As discussed above in \cref{sec:bootstrap}, BDN failed at
finding an off-shell color-dual representation satisfying 7
assumptions, and were forced to develop an on-shell notion of
color-kinematics duality \cite{Bern:2015ooa}.  Thus we must decide
which assumption(s) to break.  From both a motivation and
implementation standpoint, the simplest assumption to break is the
``power-counting'' statement, which we analyze first.

In our labeling of the two loop Jacobi-basis diagrams, shown in
\ace{Figure out fig}, we find that the power counting bound proposed
by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
terms in the double-box, and 9849 terms for the penta-triangle.
However, recent work by Ben-Shahar, Garozzo, and Johansson
\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
demonstrates that constructing Feynman rules that produce manifestly
color-dual numerators for the NMHV sector of Yang--Mills requires
introducing additional auxiliary fields, including higher-spin modes,
which could shift the expected power counting in non-trivial ways.  We
therefore attempt to find an off-shell color-dual Yang--Mills
representation in which all power counting restrictions are lifted.
